Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-06-13 article.rnw
Remove a commented-out sentence.
Clarify "in some instances" to "for some sets of species".

	\caption{%
		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
		Where results are for the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}).
		\Subref{fig:best-alpha-matrix} We show the inferred matrix of competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions (per the identified groupings).
		\Subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} We show the coclassification matrices derived from the groupings of the columns and rows, respectively.
		%These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
		Species have been reordered so that species that were grouped together appear adjacent, and the ordering is the same in all of \subref{fig:best-alpha-matrix}, \subref{fig:best-coclassification-cols}, and \subref{fig:best-coclassification-rows}.
	}
	\label{fig:best-model}
\end{figure}

% DBS: I cut out a sentence above in the caption because we say this in the text elsewhere and it's a bit unusual to refer to a later figure in the caption of an earlier one.

@@

% DBS: Can we replace "in some instances" below with something a bit more explicit? Do we mean "for some sets of species"?
The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{blonder2018hypervolume}.
% DBS: Should we consider replacing "ecological niches" above with "competitive niches"?
This could indicate that a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
Alternatively, it may suggest adopting a mixed-membership approach in which a species can belong to more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.

>>>>

	\caption{%
		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
		Where results are for the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}).
		\Subref{fig:best-alpha-matrix} We show the inferred matrix of competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions (per the identified groupings).
		\Subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} We show the coclassification matrices derived from the groupings of the columns and rows, respectively.
		Species have been reordered so that species that were grouped together appear adjacent, and the ordering is the same in all of \subref{fig:best-alpha-matrix}, \subref{fig:best-coclassification-cols}, and \subref{fig:best-coclassification-rows}.
	}
	\label{fig:best-model}
\end{figure}

@@

The intransitivity of coclassification for some sets of species even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{blonder2018hypervolume}.
% DBS: Should we consider replacing "ecological niches" above with "competitive niches"?
This could indicate that a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
Alternatively, it may suggest adopting a mixed-membership approach in which a species can belong to more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.
